---
title: "Identifier mapping using BridgeDbR"
output: html_notebook
---


# Case 1 example

We start by loading the required libraries
```{r}
library("BridgeDbR")
library("tidyverse")
```
Then we load the example data and specify the source 
```{r}
data_df <- read_tsv('data/case1-example.tsv', col_names=c('identifier'))
data_df$source = 'H'
data_df
```
We first change the default timeout so the data can be properly downloaded and then load the data for the organism we are mapping from. 
We then use the maps method to map our data to all possible other data sources.
```{r}
options(timeout=300)
location <- getDatabase('Homo sapiens')
mapper <- loadDatabase(location)
maps(mapper, data_df)
```
If we only want to map to a specific data source we can also do that by specifying in the maps method as follows
```{r}
maps(mapper, data_df, target='En')
```
# Case 2 example
Here we load the data specifying the column names
```{r}
data_df <- read_tsv('data/case2-example.tsv', col_names=c('local', 'identifier'))
data_df$source = 'H'
data_df
```
Now as before we can map either by specifying the target data source or not
```{r}
mapping = maps(mapper, data_df, target='En')
mapping
```
And we join it with our local identifiers
```{r}
right_join(data_df, mapping)
```

